Wikipedia Text Mining and Entropy Analysis

### 2018-10-05 wiki_entropy.Rmd
Fixed differing n problem

#get_slopes("not child", 6, py$xmf_df, "gloss")
gtx <- extract_wiki_tokens(6, 25, xmf_df) %>% filter(word != " ") %>% filter(word != "")

tokens %>%
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = n()) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

>>>>

gtx <- extract_wiki_tokens(6, 1000, xmf_df)

gtx %>%
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats
